Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-12-22 paper.tex
update toc & main

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
%% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}

@@

\begin{tocentry}
  \centering
 \includegraphics[height=3.5cm]{img/toc.pdf}
\end{tocentry}

@@

\begin{abstract}
  The dielectric constant, which defines the polarization of
  the media, is a key quantity in condensed matter. It determines
  several electronic and optoelectronic properties important for a
  plethora of modern technologies, and its importance of 
  % from computer memory to field effect
  % transistors and communication circuits. Moreover, the importance of
  % the dielectric constant in
  describing electromagnetic interactions through screening plays a
  critical role in understanding fundamental molecular
  interactions. Here we show that despite its fundamental
  transcendence, the dielectric constant does not define unequivocally
  the dielectric properties of two-dimensional (2D) materials due to
  the locality of their electrostatic screening. Instead, the
  electronic polarizability correctly captures the dielectric nature
  of a 2D material which is united to other physical quantities in an
  atomically thin layer. Being a quantity with unique definition, the
  electronic polarizability overcomes the disadvantage of uncertainty
  posed by the effective dielectric constant model conventionally used
  to described screening in 2D material systems.  Furthermore, we
  reveal a long-sought universal formalism where electronic,
  geometrical and dielectric properties are intrinsically correlated
  through the polarizability opening the door to probe quantities yet
  not directly measurable including the real covalent thickness of a
  layer. Lastly, we unify the concept of dielectric properties in any
  material dimension finding a global dielectric anisotropy index
  defining their controllability through dimensionality.
\end{abstract}

@@

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgaps\cite{Moss_1950_relation,Moss_1985_n_Eg}, 
optical absorption\cite{kittel_2005_introduction} and 
conductivities\cite{Dressel_2001_electrodynamics}   
with elemental interactions. 
The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an 
electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. Such definitions determine a broad range of 
condensed matter physics, as well as in related fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in bulk materials is well established via different 
theoretical \cite{Adler_1962,Hybertsen_1987} and experimental techniques \cite{palik_1998handbook} of distinct flavors
% where the probe of the dielectric properties 
% is made through an external electric field. 
%
Despite its obvious appeal, however, it is still unknown whether such quantity can determine the 
% electronic and
dielectric properties of two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
The confined nature of such atomically-thin 2D crystals associated
with the attenuated and anisotropic character of the dielectric
screening
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
have generated long-standing debates whether the dielectric constant
truly represents dielectric features of such low-dimensional systems,
% or it can be used only as an
% additional parameter from the bulk-counterparts.
The controversy of
$\varepsilon$ values reported by both theoretical and experimental
approaches can be widely seen throughput literature\cite{Li_2016},
where the variation of $\varepsilon$ can be more than one order of
magnitude. As a consequence, several key physical parameters that
scales with $\varepsilon$, such as the exciton binding energy and
Debye screening length, cannot be reliably estimated due to the
discrepancy of reported $\varepsilon$ values. In this letter, we give
a thorough study of the underlying issue. Using \textit{ab initio}
simulations of a model system, we demonstrate that the macroscopic
dielectric constant strongly depends on the size of the superlattice,
making it unsuitable to describe the screening of a 2D material. On
the contrary, by analyzing the formalism of dielectric tensors, we
propose that the electronic polarizability is the true descriptor
which uniquely captures the dielectric nature of 2D materials. The 2D
electronic polarizability has unique definition, which overcomes the
disadvantage of ambiguity compared with the conventionally used
effective dielectric medium model for 2D materials. Moreover, we show
the universal scaling relations for in- and out-of-plane 2D electronic
polarizabilities with the electronic and geometric information of the
2D material. The concept of electronic polarizabilities bridges the
gap between the dielectric properties of 2D and 3D systems, and can be
extended to characterize the dielectric anisotropy for any material
dimensions.

@@

We first approach the discrepancy of macroscopic dielectric constant
of 2D materials, by showing that the current definition of
$\varepsilon$ used in layered materials is ill defined.  This can be
viewed in a model system as illustrated
in Figure \ref{fig-1}, where an isolated 2D material is placed in
the \textit{xy}-plane of a periodically repeating superlattice (SL)
with a length $L$ along the \textit{z}-direction separating the cell
images. The static macroscopic dielectric tensor from the superlattice
$\varepsilon_{\mathrm{SL}}^{pq}$, is determined through fundamental
electrostatics by the response of the polarization density
$\boldsymbol{P}^{p}$ under small perturbative external field
$\boldsymbol{E}^{q}$, where $p$, $q$ are the directions of
polarization and electric field,
respectively~\cite{Dressel_2001_electrodynamics}:
\begin{subequations}
  \begin{eqnarray}
      \label{eq:def-eps-1}
    &\varepsilon_{\mathrm{SL}}^{pq} &= \kappa^{pq} +
                                 {\displaystyle \frac{\partial \boldsymbol{P}^{p}}
                                 {\varepsilon_{0} \partial \boldsymbol{E}^{q}}} \\
          \label{eq:def-eps-2}
    &\boldsymbol{P}^{p} &=  {\displaystyle \frac{\boldsymbol{u}^{p}}{\Omega}}
                          = {\displaystyle \frac{{\displaystyle
          \int_{\mathrm{SL}} \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}}
                          {AL}}
  \end{eqnarray}
\end{subequations}
where $\kappa$ is the dielectric tensor of the environment,
$\boldsymbol{u}$ is the total dipole moment within the SL, $\rho$ is
the spatial charge density, $\Omega=AL$ is the volume of the
supercell, $A$ is the \textit{xy}-plane area of the SL and
$\varepsilon_{0}$ is vacuum permittivity. Here we limit out study on
the electronic contribution to the macroscopic dielectric constant
where the dipole $\boldsymbol{P}$ comes from the displacement of
electrons under external field.  On the other hand, the ionic
contribution to $\varepsilon_{\mathrm{SL}}$ that comes from
displacement of atomic nuclei is not covered in this due to its
complex dependency on several factors including phonon
dispersion~\cite{Sohier_2017} as well as lattice
symmetry~\cite{Laturia_2018}, which requires separated discussions.
The symmetry of 2D materials lead to the negligible off-diagonal
elements of the dielectric tensor ($p \neq q$), while and diagonal
elements $\varepsilon_{\mathrm{SL}}^{xx}$,
$\varepsilon_{\mathrm{SL}}^{yy}$ and $\varepsilon_{\mathrm{SL}}^{zz}$
can be different \cite{Sohier_2016}.  Considering that the 2D material
is placed in vacuum ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can
distinguish two components of $\varepsilon_{\mathrm{SL}}$, namely the
in-plane ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constants, where
$\varepsilon_{\mathrm{SL}}^{\parallel} =
(\varepsilon_{\mathrm{SL}}^{xx} + \varepsilon_{\mathrm{SL}}^{yy})/2$
and
$\varepsilon_{\mathrm{SL}}^{\perp} = \varepsilon_{\mathrm{SL}}^{zz}$.
The absence of bonding perpendicular to the plane confines the induced
dipoles along the \textit{z}-direction within a range of $\sim{}$5--6
\AA{} into the vacuum (Figure \ref{fig-1}{\textbf a} and Supplementary
Figure \ref{SI-fig:rho-profile}).
Under a certain external field, when $L$ increases, the confinement of
the induced dipole moment $\boldsymbol{u}$ causes the integral in the
numerator of Eq.~\ref{eq:def-eps-2} to be saturated, when the
separation is large enough such that dipole moment from periodic
images do not mutually interfere. On the other hand, the increase of
$L$ in the denominator of Eq.~\ref{eq:def-eps-2} dilutes the polarization density, and in turn makes both
$\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ dropping to
unity when $L$ is infinitely large.
% In the case of bulk materials
% such physical dependence is well described given the periodicity of
% the 3D crystal throughout the space.
%since this volume is used to represent the crystal 
%periodically throughout the space.  
% In the case of 2D materials, however, such repetition is artificial along the direction 
% perpendicular to the plane.
Despite of the simplicity of this argument, any calculation performed
using such definition will intrinsically depend on the magnitude of
$L$, an artificial parameter introduced by simulation system. This
dependence can be clearly demonstrated by plotting
$\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ calculated from density functional
theory (DFT) (see {\it Theoretical Methods} for details) as a function
of $L$ for P\={6}m2 transition metal dichalcogenides (TMDCs),
2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te (top panels of Figure
\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c}, respectively). To
get a better description of the electronic band structure, the
calculations of dielectric properties were performed at the level of
Heyd-Scuseria-Ernzerhof (HSE06) hybrid functional
\cite{Heyd_2003,Heyd_2006}.  Both components of the dielectric
constant decreases with $L$ as excepted. To rule out the possibility
that the result is affected by the choice of \textit{ab initio}
methods, we also performed simulations at higher levels of theory
using many-body techniques (G$_{0}$W$_{0}$), which invariably give
alike results (see Supplementary Figure \ref{SI-fig:GW-PBE-alpha}).
The lattice-size dependency also exists for dielectric function in the
frequency ($\omega$) domain. We carried out similar analysis for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ using different levels
of techniques, including Perdew-Burke-Ernzerhof (PBE)
exchange-correlation functional
\cite{Perdew_1996,Ernzerhof_1999,Paier_2005}, many-body Green function
method (G\textsubscript{0}W\textsubscript{0})~\cite{Hedin_1965} and
Bethe-Salpethe equation (BSE)~\cite{Onida_2002}, with increasing
accuracy of calculated optical properties (PBE $<$
G\textsubscript{0}W\textsubscript{0} $<$ BSE) due to including of
many-body screening and excitonic effects (details see Supplementary
Section \ref{SI-ssec:gw}). Despite various levels of theory involved,
the magnitude of dielectric functions calculated universally decreases
with $L$ over the frequency domain.  These results indicate that
quantities that depend on
$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, including the optical
absorption (abs., equivalent to $\mathrm{Im}(\varepsilon_{\mathrm{SL}}(\omega))$), refractive index ($n$,  $\sim{}\sqrt{\mathrm{Re}(\varepsilon_{\mathrm{SL}})}$) and electron energy loss spectrum (EELS, equivalent to $-1 / \mathrm{Im}(\varepsilon_{\mathrm{SL}}(\omega))$), suffers the same
deficiencies as $\varepsilon_{\mathrm{SL}}$ for 2D materials. This
simple model system explains the origin of the discrepancy of
dielectric constant values reported in previous
literature~\cite{Li_2016}.
%%%
% We observe that neither
% $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
% $\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
% that the long-range Coulomb interaction could not be completed
% screened within the range of magnitudes computationally accessible
%.
%As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
%it impractical to represent the dielectric nature of a 2D material
%both theoretically and experimentally, because the size of vacuum
%layer must always be considered. 

@@

Our results show that the 2D electronic polarizability
$\alpha_{\mathrm{2D}}$ is a local variable determining the dielectric
properties of 2D materials.  There exist well defined relationships
between $\alpha_{\mathrm{2D}}$ and other quantities hidden in the
electronic properties.  According to our analysis, simple scaling
equations involving bandgaps and layer thicknesses can be used to
describe both dielectric and electronic features at the same
footing. A dielectric anisotropy index is found relating any material
dimension with its controllability.  Thus, our results suggest that
the challenge of understanding the dielectric phenomena is in general
a geometrical problem mediated by the bandgap. We believe the
principles presented here will benefit both fundamental understanding
of 2D materials as well as rational device design and optimization.

@@

\section{Data Availability}
The data that support the findings of this study are available from
the corresponding author upon reasonable request.

>>>>

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Victoria, VIC 3216, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland}
\author{Manish Chhowalla}
%% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kingdom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\date{}
\title{Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials}
%\title{The Unified Nature of the Dielectric Properties of Two-Dimensional Materials}
% \title{Unified Understanding of the Dielectric Nature of Two-Dimensional Materials}

@@

% \begin{tocentry}
 % \centering
% \includegraphics[width=0.70\linewidth]{img/toc_v121719.pdf}  %toc.pdf  
% \end{tocentry}
%
%
%  \includegraphics[width=0.70\linewidth]{img/fig1.pdf}

@@

\begin{abstract}
  The dielectric constant, which defines the polarization of
  the media, is a key quantity in condensed matter. It determines 
  several electronic and optoelectronic properties important for a 
  plethora of modern technologies 
  from computer memory to field effect
  transistors and communication circuits. Moreover, the importance of
  the dielectric constant in 
  describing electromagnetic interactions through screening plays a
  critical role in understanding fundamental molecular
  interactions. Here we show that despite its fundamental
  transcendence, the dielectric constant does not define unequivocally
  the dielectric properties of two-dimensional (2D) materials due to
  the locality of their electrostatic screening. Instead, the
  electronic polarizability correctly captures the dielectric nature
  of a 2D material which is united to other physical quantities in an
  atomically thin layer. 
 %
  %
%  Being a quantity with unique definition, the
%  electronic polarizability overcomes the disadvantage of uncertainty
%  posed by the effective dielectric constant model conventionally used
%  to described screening in 2D material systems.  
  We reveal a long-sought universal formalism where electronic, 
  geometrical and dielectric properties are intrinsically correlated  
  through the polarizability opening the door to probe quantities yet  
  not directly measurable including the real covalent thickness of a 
  layer. We unify the concept of dielectric properties in any 
  material dimension finding a global dielectric anisotropy index
  defining their controllability through dimensionality. 
\end{abstract}

@@

The dielectric constant $\varepsilon$ (also known as the relative permittivity) 
plays a crucial role in bridging various fundamental material
properties, such as bandgap \cite{Moss_1950_relation,Moss_1985_n_Eg}, 
optical absorption\cite{kittel_2005_introduction} and 
conductivity \cite{Dressel_2001_electrodynamics}   
with elemental interactions. 
The central place of $\varepsilon$ in solid-state physics drives the analysis of several phenomena 
where is common to classify a material accordingly to its ability to screen an 
electric field $\boldsymbol{E}$ in terms of insulators, metals and semiconductors. 
Such definitions determine a broad range of 
condensed matter physics, as well as in related 
fields in chemistry and materials science. 
The ability to compute and measure $\varepsilon$ in 
bulk materials is well established via different 
theoretical \cite{Adler_1962,Hybertsen_1987} and 
experimental techniques \cite{palik_1998handbook} of distinct flavors
where the probe of the dielectric properties 
is made through an external electric field. 
%
Despite its obvious appeal, however, it is 
still unknown whether such quantity can determine the 
electronic and dielectric properties of 
two-dimensional (2D) materials \cite{Novoselov_2016}.  
%
The confined nature of such atomically-thin 2D crystals associated
with the attenuated and anisotropic character of the dielectric
screening
\cite{Keldysh_1979_eps_multi,Sharma_1985,Low_2014_screening_BP,Cudazzo_2011_screening_2D,Bechstedt_2012,Cudazzo_2010_screen2D,Nazarov_2015_2D_3D}
has generated long-standing debates whether the dielectric constant
truly represents the dielectric features of such low-dimensional systems. 
%or it can be used only as an
%additional parameter from the bulk-counterparts.
%
%
The controversy of values
reported by both theoretical and experimental
approaches can be widely seen throughout the specialized 
literature, see Ref.\cite{Li_2016} for a summary,
where the variation of $\varepsilon$ can be more than one order of
magnitude. As a consequence, several key physical parameters that
scale with $\varepsilon$, such as the exciton binding energy and
Debye screening length, cannot be reliably estimated due to the
discrepancy of the reported magnitudes of $\varepsilon$.

Here, by using a combination of analytical and numerical models liaised with 
highly-accurate first-principles methods involving high-throughput screening 
techniques, we show that the dielectric constant does not provide a reliable
description of the screening features of a 2D material. The interplay between local 
electrostatic interactions in the monolayer and the volume dependence 
in the definition of $\varepsilon$ makes such quantity questionable. 
%
%
We propose however that the electronic polarizability that describes 
the electron dipole in the 2D material as the true descriptor 
of its dielectric nature. 
%
%
We overcome several problems intrinsic to thin layers not achievable using conventional 
effective dielectric medium models, such as the real thickness of a monolayer and 
any dependence on the long-range Coulomb potential. 
We unveil universal scaling relations between electronic and dielectric properties through 
the electronic polarizability, such as band gaps, optical spectra and exciton radius, for the 
current library of known 2D materials involving different lattice symmetries, 
atomic elements and chemical and physical properties. 
%
Moreover, the concept of electronic polarizabilities bridges the
gap between the dielectric properties of 2D and 3D systems through a novel 
dielectric anisotropy index that generalized the concept of dielectric control 
using dimensionality and bandgap. 
Our results open a new avenue for the study of the 
dielectric properties of 2D compounds using techniques yet to be explored.

%and can be
%extended to characterize the dielectric anisotropy for any material
%dimensions.

@@

We first approach the discrepancy of macroscopic dielectric constant
of 2D materials, by showing that the current definition of
$\varepsilon$ used in layered materials is {ill-defined}.  This can be
viewed in a model system as illustrated
in Figure \ref{fig-1}, where an isolated 2D material is placed in
the \textit{xy}-plane of a periodically repeating superlattice (SL)
with a length $L$ along the \textit{z}-direction separating the cell
images. The static macroscopic dielectric tensor from the superlattice
$\varepsilon_{\mathrm{SL}}^{pq}$, is determined through fundamental
electrostatics by the response of the polarization density
$\boldsymbol{P}^{p}$ under small perturbative external field
$\boldsymbol{E}^{q}$, where $p$, $q$ determine their directions,
respectively~\cite{Dressel_2001_electrodynamics}:
\begin{subequations}
  \begin{eqnarray}
      \label{eq:def-eps-1}
    &\varepsilon_{\mathrm{SL}}^{pq} &= \kappa^{pq} +
                                 {\displaystyle \frac{\partial \boldsymbol{P}^{p}}{\varepsilon_{0} \partial \boldsymbol{E}^{q}}} \\
          \label{eq:def-eps-2}
    &\boldsymbol{P}^{p} &=  {\displaystyle \frac{\boldsymbol{u}^{p}}{\Omega}}
                          = {\displaystyle \frac{{\displaystyle
          \int_{\mathrm{SL}} \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}}{AL}}
  \end{eqnarray}
\end{subequations}
where $\kappa$ is the dielectric tensor of the environment,
$\boldsymbol{u}$ is the total dipole moment within the SL, $\rho$ is
the spatial charge density, $\Omega=AL$ is the volume of the
supercell, $A$ is the \textit{xy}-plane area of the SL and
$\varepsilon_{0}$ is vacuum permittivity. Here we limit our study on
the electronic contributions to the macroscopic dielectric constant
where the dipole $\boldsymbol{P}$ results from the response 
of the electron density under an external field.  
Ionic contributions\cite{Sohier_2017} to $\varepsilon_{\mathrm{SL}}$ 
have previously been shown to be negligible\cite{relax-epsilon} and 
are not considered here.  
%
%On the other hand, the ionic
%contribution to $\varepsilon_{\mathrm{SL}}$ that comes from
%displacement of atomic nuclei is not covered in this due to its
%complex dependency on several factors including phonon
%dispersion~\cite{Sohier_2017} as well as lattice
%symmetry~\cite{Laturia_2018}, which requires separated discussions.
The symmetry of 2D materials leads to inappreciable off-diagonal
elements of the dielectric tensor ($p \neq q$), while the diagonal
elements $\varepsilon_{\mathrm{SL}}^{xx}$,
$\varepsilon_{\mathrm{SL}}^{yy}$ and $\varepsilon_{\mathrm{SL}}^{zz}$
can be different \cite{Sohier_2016}.  
%
Considering that the 2D material
is placed in vacuum ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can
distinguish two components of $\varepsilon_{\mathrm{SL}}$, namely the
in-plane ($\varepsilon_{\mathrm{SL}}^{\parallel}$) and out-of-plane
($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constants, where
$\varepsilon_{\mathrm{SL}}^{\parallel} =
(\varepsilon_{\mathrm{SL}}^{xx} + \varepsilon_{\mathrm{SL}}^{yy})/2$
and
$\varepsilon_{\mathrm{SL}}^{\perp} = \varepsilon_{\mathrm{SL}}^{zz}$.
The absence of bonding perpendicular to the plane confines the induced
dipole moments along the \textit{z}-direction within a range of $\sim$5--6
\AA{} into the vacuum (Figure \ref{fig-1}{\textbf a} and Supplementary
Figure \ref{SI-fig:rho-profile}).
%
%
Under a given external field, the strong confinement of
the induced dipole moment $\boldsymbol{u}$ causes the integral in the 
numerator of Eq.~\ref{eq:def-eps-2} to be converged within few \AA's 
resulting that the dipole moment from the periodic supercell 
images do not mutually interfere. 
%

Conversely, the increase of
$L$ in the denominator of Eq.~\ref{eq:def-eps-2} dilutes the 
polarization density, and in turn makes both
$\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ dropping to
unity when $L$ is infinitely large, which is not physical. 
% In the case of bulk materials
% such physical dependence is well described given the periodicity of
% the 3D crystal throughout the space.
%
%since this volume is used to represent the crystal 
%periodically throughout the space.  
%
%
% In the case of 2D materials, however, such repetition is artificial along the direction 
% perpendicular to the plane.
Despite the simplicity of this argument, any calculation performed
using such definition will intrinsically depend on the magnitude of
$L$, an artificial parameter introduced by the simulation setup. This
dependence can be clearly demonstrated by plotting
$\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ calculated from density functional
theory (DFT) (see {\it Theoretical Methods} for details) as a function
of $L$ for P\={6}m2 transition metal dichalcogenides (TMDCs),
2H-MX$_{2}$, where M=Mo, W and X=S, Se, Te (top panels of Figure
\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c}, respectively). To
obtain a better description of the electronic band structure, the
calculations of dielectric properties were performed at the level of
Heyd-Scuseria-Ernzerhof (HSE06) hybrid functional
\cite{Heyd_2003,HSE_2006}.  Both components of the dielectric
constant decrease with $L$ as excepted. To rule out the possibility
that the result is affected by the choice of the functional, 
we performed simulations at higher levels of theory
using many-body techniques (G$_{0}$W$_{0}$), which invariably give
alike results (see Supplementary Figure \ref{SI-fig:GW-PBE-alpha}).
The lattice-size dependency also exists for the dielectric function in the 
frequency domain.

\begin{figure}[H]
\centering
\includegraphics[width=0.70\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} \textbf{2D polarizability and the breakdown of
    effective dielectric model
    (EDM)} % \textbf{2D polarizability as the
  % true descriptor of the dielectric nature of 2D materials.}
  \textbf{a,} 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS\textsubscript{2} in a periodic superlattice under
  external eletric field of 0.01 V/\AA{}.  The green and red regions
  represent negative and positive induced charges, respectively. The
  macroscopic $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities
  $\alpha_{\mathrm{2D}}^{\parallel}$ and
  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant to $L$.
  \textbf{b,} $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. 
  \textbf{c,} $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. 
  %
  %
  {\bf d-e,} Estimated $\varepsilon_{\mathrm{2D}}^{\parallel}$ and 
  $\varepsilon_{\mathrm{2D}}^{\perp}$, respectively, using EDM  
  as a function of the uncertainty of the effective layer
  thickness $\delta^{*}_{\mathrm{2D}}$. The inset in {\bf e,} shows schematically the main parameters
  utilized in EMD: the vacuum layer ($\varepsilon^{}_{\mathrm{0}}$), an approximate thickness of the layer   which is given by $\delta^{*}_{\mathrm{2D}}$, and the obtained $\varepsilon^{}_{\mathrm{2D}}$. The length of the box perpendicular to the surface of the layer is given by $L$ (not shown). 
  %
  Overall, there is a large variation and associated errors
  to both components of the dielectric constant for small changes of $\delta^{*}_{\mathrm{2D}}$ in the range of $\pm7.5$\%.  
  %
  % HSE06 functional is used in all plots.
}
\end{figure}

We carried out similar analysis for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ using different 
approaches including Perdew-Burke-Ernzerhof (PBE)
exchange-correlation functional
\cite{Perdew_1996,Ernzerhof99,Paier_2005_PBE}, 
G\textsubscript{0}W\textsubscript{0}\cite{Hedin_1965} and
Bethe-Salpeter equation (G\textsubscript{0}W\textsubscript{0}$-$BSE)\cite{Onida_2002} (see Supplementary Section \ref{SI-ssec:gw} and 
Supplementary Figures \ref{SI-fig:PBE-omega-in}$-$\ref{SI-fig:BSE-omega-out}). 
%
%with increasing
%accuracy of calculated optical properties (PBE $<$
%G\textsubscript{0}W\textsubscript{0} $<$ BSE) due to including of
%many-body screening and excitonic effects (details see Supplementary
%Section \ref{SI-ssec:gw}). 
%
Despite the various levels of theory analyzed and the increased 
accuracy of the calculated optical properties due to the inclusion of 
many-body screening and excitonic effects, 
the magnitude of the dielectric function universally decreases
with $L$ over the frequency. The underlying physical reason for such 
dependence can be noticed in the definition of the dielectric 
function versus $\omega$ shown in Eqs. \ref{SI-eq:dft-dielectric}$-$\ref{SI-eq:dft-dielectric-real}, which also depend on the volume of the unit cell. 
%
These results indicate that any 
quantity that depends on
$\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, such as the optical
absorption ($\mathrm{Im}\{\varepsilon_{\mathrm{SL}}(\omega)\}$), refractive index ($n=\sqrt{\mathrm{Re}\{\varepsilon_{\mathrm{SL}}\}}$) and electron energy loss spectrum (EELS, $\mathrm{Im}\{-1/\varepsilon_{\mathrm{SL}}(\omega)\}$), suffers the same deficiencies for 2D materials.

@@

Our results show that the 2D electronic polarizability
$\alpha_{\mathrm{2D}}$ is a local variable determining the dielectric
properties of 2D materials.  There exist well-defined relationships
between $\alpha_{\mathrm{2D}}$ and other quantities hidden in the
electronic properties.  According to our analysis, simple scaling
equations involving bandgap and layer thickness can be used to
describe both dielectric and electronic features at the same
footing. A dielectric anisotropy index is found relating any material
dimension with its controllability.  Thus, our results suggest that
the challenge of understanding the dielectric phenomena is in general
a geometrical problem mediated by the bandgap. We believe the
principles presented here will benefit both fundamental understanding
of 2D materials as well as a rational device design and optimization.

@@

\section*{Data Availability}
The data that support the findings of this study 
is available within the paper and its Supplementary Information.

\subsubsection*{Competing interests}
The Authors declare no conflict of interests.

\subsubsection*{Acknowledgments}
C.J.S. and T.T. are grateful for financial support from ETH startup funding. 
L.H.L. thanks the financial support from Australian Research Council (ARC) 
via Discovery Early Career Researcher Award (DE160100796). 
E.J.G.S. acknowledges the use of computational resources from the UK 
Materials and Molecular Modelling Hub for access to THOMAS 
supercluster, which is partially funded by EPSRC (EP/P020194/1); and CIRRUS Tier-2 HPC 
Service (ec019 Cirrus Project) at EPCC (http://www.cirrus.ac.uk) funded 
by the University of Edinburgh and EPSRC (EP/P020267/1). 
The Department for the Economy (USI 097) is acknowledged for funding support.

\subsubsection*{Author Contributions}
E.J.G.S. conceived the idea and supervised the project. 
T.T., D.S., D.H. and E.J.G.S. performed the first-principles simulations 
and data analytics. T.T. developed the analytical model with 
inputs from E.J.G.S. and C.J.S. L.H.L. and J.N.C. 
performed numerical analysis and contributed to the discussions together with M.C.
E.J.G.S. and T.T. co-wrote the manuscript with inputs from all authors. 
All authors contributed to this work, read the manuscript, discussed 
the results, and all agree to the contents of the manuscript.

\section*{Supporting Information}

The Supporting Information contains detailed descriptions and
discussions about dielectric properties of 2D materials, effective
dielectric model, derivations of the 2D polarizability-based model,
dependency of $\alpha_{\mathrm{2D}}$ on the choice of bandgap,
relation between 2D and 3D properties, explanations of the dielectric
anisotropy, as well as raw data sheet from first principles
calculations.
